Literature Review

### 2020-07-02 Literature_review.tex

@@

@@

\item (Question: Is there anything about uncertainty in this paper?)
\item Answer: There is, the second and third bullet point has an overview of the way the paper treats uncertainty.

@@

>>>>

\section{Papers related to Ideal Point Models}

@@

\item For each state, we estimate one- and two-dimensional spatial models using the Bayesian item response model.We beginwith an examination of the predictive power of the spatial model for explaining patterns of roll call voting within each state

@@

@@

\section{Papers not related to Ideal Point Models}
